Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2020-11-01 main.tex
:art: Illustrate block diagonal matrix

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
% \usepackage{caption}
\usepackage{cite}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize]{subfig}
% \usepackage[cmintegrals]{newtxmath}
\usepackage[short]{optidef}

\interdisplaylinepenalty=2500
\pgfplotsset{compat=newest}
\usetikzlibrary{plotmarks}
\usetikzlibrary{arrows.meta}
\usepgfplotslibrary{patchplots}
\newtheorem{proposition}{Proposition}
\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}

@@

\begin{document}
	\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
	\author{
		\IEEEauthorblockN{
			Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
			~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
			and~Zhenyuan~Feng,~\IEEEmembership{Member,~IEEE}
		}
		\thanks{
			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx, zhenyuan.feng19\}@imperial.ac.uk).
		}
	}
	\maketitle

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates propagation loss and boosts energy efficiency by adaptive passive beamforming. This paper investigates an IRS-aided Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on a practical nonlinear energy harvester model, where a multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS. Considering rectifier nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. Stationary solutions are achieved based on Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by Geometric Programming (GP) technique. It is confirmed that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH), such that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR). Simulation results also show that the introduction of IRS significantly enlarges the R-E region while preserving the waveform preference and transceiving strategy. Although the AP-IRS-user extra link is relatively weak, we found that the information and power benefits of passive beamforming scale much faster than those of active beamforming. It suggests using more active antennas for small-scale SWIPT and more passive elements for large-scale SWIPT.
	\end{abstract}

@@

			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the rectifier input power level. It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then implemented joint waveform and beamforming design for WPT. Simulation and experiments demonstrated the inaccuracy of the rectenna linear model and emphasized the benefit of modeling the rectifier nonlinearity in real system design \cite{Kim2019,Kim2020a}. Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand operation range. Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}. Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of power splitting and time sharing is in general the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?". This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g. modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
		\end{subsection}

@@

		\begin{subsection}{IRS-Aided SWIPT}
			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT. It was argued in \cite{Wu2020b} that dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system. On the other hand, \cite{Tang2019} suggested that if the interference can be cancelled, multiple energy beams are generally required for the max-min harvested power problem. \cite{Wu2020a} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated. In such cases, a single energy stream is enough for all energy receivers.

			However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission based on an oversimplified linear harvester model for separated information and energy receivers. Rectifier nonlinearity and co-localized receiver, acknowledged as key to practical and efficient SWIPT system design, have not yet been addressed in the relevant research. In this paper, we marry the benefits of joint waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS. The contribution of the paper are listed as follows.

			\textit{First}, we introduce a novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design. This architecture can be seen to IRS-aided SWIPT what \cite{Clerckx2018b} is to SWIPT. Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user. A multi-carrier unmodulated power waveform (deterministic multisine) is superposed to a multi-carrier modulated information waveform to boost the energy transfer efficiency. The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS, and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity. This is the first paper to proposed such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT. Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2020} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design. On the contrary, this paper focus on multi-carrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.

			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design so as to characterize the R-E region achieved by the proposed architecture. The R-E region characterization problem is transformed into multiple energy maximization problems subject to different rate constraints. Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform and active beamforming at the transmitter and power splitting ratio at the receiver, until convergence. On top of the SWIPT optimization based on Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs an low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in a efficient and reliable manner. Despite no rigorous mathematical proof exists for the convergence of the relaxed IRS phase shift problem, numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.

@@

			\textit{Notations:} Scalars are denoted by italic letters, vectors are denoted by bold lower-case letters, and matrices are denoted by bold upper-case letters. $j$ refers to the imaginary unit. $\mathbb{C}^{x \times y}$ denotes the subspace spanned by complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ stand for the real and imaginary part of a complex number or variable, respectively. $(\cdot)^*$, $(\cdot)^T$ and $(\cdot)^H$ represent the conjugate, transpose, and conjugate transpose operators, respectively. $\mathcal{A}\{\cdot\}$ extracts the DC component of a signal, and $\mathcal{E}_X\{\cdot\}$ takes the expectation over the distribution of the random variable $X$ ($X$ may be omitted for simplicity). For a scalar $x$, $\lvert{x}\rvert$ denotes its absolute value. For a vector $\boldsymbol{x}$, $\lVert{\boldsymbol{x}}\rVert$ refers to its Euclidean norm, $\arg(\boldsymbol{x})$ refers to its argument vector, and $\mathrm{diag}(\boldsymbol{x})$ refers to a square diagonal matrix with the elements of $\boldsymbol{x}$ on the main diagonal. For a general matrix $\boldsymbol{M}$, $\mathrm{rank}(\boldsymbol{M})$ denotes it rank. For a square matrix $\boldsymbol{S}$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite. The distribution of a random vector consists of Circularly Symmetric Complex Gaussian (CSCG) variables is denoted by $\mathcal{CN}(\boldsymbol{\mu},\boldsymbol{\Sigma})$, where $\boldsymbol{\mu}$ is the mean vector and $\boldsymbol{\Sigma}$ is the covariance matrix. $\sim$ means "distributed as". We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as stationary solution and solution at iteration $i$, respectively.
		\end{subsection}
	\end{section}

@@

		\begin{subsection}{Transmit Signal}
			Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$, which follows an i.i.d. CSCG distribution with zero mean and unit variance, namely $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$. The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
			\begin{equation}\label{eq:x_m}
				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n,m}\tilde{x}_{I,n}(t)}+w_{P,n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{I/P,n,m}$ denotes the weight of the information and power signal transmitted by antenna $m$ at subband $n$. Define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ by stacking up weights across all antennas. Therefore, the transmit information and power signals write as
			\begin{align}
				\boldsymbol{x}_{I}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\,,\label{eq:x_I}\\
				\boldsymbol{x}_{P}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}}\,.\label{eq:x_P}
			\end{align}
		\end{subsection}

		\begin{subsection}{Composite Channel}
			At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection amplitude $\gamma_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\gamma_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries. The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel. On top of this, the total composite channel is obtained by superposing the IRS-aided extra channel to the AP-user direct channel as
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{D,n}^H + \boldsymbol{h}_{R,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where $\boldsymbol{\phi}=[\gamma_1 e^{j \theta_1}, \dots, \gamma_L e^{j \theta_L}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
		\end{subsection}

@@

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the multisine power waveform creates no interference to the information waveform. Therefore, the achievable rate writes as
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
			\end{equation}
			where $\rho$ is the power splitting ratio for the energy harvester, $\sigma_n^2$ is the variance of the total noise (at RF-band and during RF-to-baseband conversion) on tone $n$. Rate \ref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
		\end{subsection}

@@

			To maximize non-concave expression \ref{eq:z_irs}, we propose a SCA algorithm that approximate the second-order terms by first-order Taylor expansion \cite{Adali2010}. Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are

@@

			which provide lower bounds to the corresponding terms in \ref{eq:z_irs}. Hence, the objection function is approximated by $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ in \ref{eq:z_irs_approx}, and problem~\ref{op:original} is transformed to

@@

			Therefore, problem~\ref{op:original} is reduced to an amplitude optimization issue

@@

			Since problem~\ref{op:waveform} involves the production of nonnegative real variables, we introduce auxiliary variables $t',\bar{\rho}$ and transform it into a reversed GP

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
% \usepackage{caption}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize]{subfig}
% \usepackage[cmintegrals]{newtxmath}
\usepackage[short]{optidef}

\interdisplaylinepenalty=2500
\pgfplotsset{compat=newest}
\usetikzlibrary{plotmarks}
\usetikzlibrary{arrows.meta}
\usepgfplotslibrary{patchplots}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}
\usetikzlibrary{arrows,matrix,positioning}

@@

\begin{document}
	%\title{IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
	%\title{Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer: Joint Waveform, Active and Passive Beamforming Design}
	%\title{Joint Waveform, Active and Passive Beamforming Design for Intelligent Reflecting Surface-Aided Wireless Information and Power Transfer}
	%\title{Joint Waveform, Active and Passive Beamforming Design for Intelligent Reflecting Surface-Aided SWIPT}
	\title{Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design}
	\author{
		\IEEEauthorblockN{
			Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
			~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
			and~Zhenyuan~Feng,~\IEEEmembership{Member,~IEEE}
		}
		\thanks{
			The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx, zhenyuan.feng19\}@imperial.ac.uk).
		}
	}
	\maketitle

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly restricted by the strength of the received Radio-Frequency (RF) signal. To tackle this problem, we introduce a low-power Intelligent Reflecting Surface (IRS) that compensates the propagation loss and boosts the energy efficiency by provide a passive beamforming gain. This paper investigates an IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna user under the assist of an IRS. Considering the rectifier nonlinearity, we aim to maximize the Rate-Energy (R-E) region through a joint optimization of the transmit waveform and active beamforming at the AP, the reflection coefficients at the IRS, and the power splitting ratio at the user. Stationary solutions are achieved based on Alternating Optimization (AO) technique, where the optimal active beamforming is obtained in closed form, the passive beamforming is optimized by Successive Convex Approximation (SCA) technique, and the waveform and splitting ratio are optimized by Geometric Programming (GP) technique. It is confirmed that due to rectifier nonlinearity, a dedicated power signal can be beneficial to energy harvesting (EH), such that the Time-Switching (TS) receiver is preferred over Power-Splitting (PS) receiver for multi-carrier transmission at a low Signal-to-Noise Ratio (SNR). Simulation results also show that the introduction of IRS significantly enlarges the R-E region while preserving the waveform preference and transceiving strategy. Although the AP-IRS-user extra link is relatively weak, we found that the information and power benefits of passive beamforming scale much faster than those of active beamforming. It suggests using more active antennas for small-scale SWIPT and more passive elements for large-scale SWIPT.
	\end{abstract}

@@

			The concept of SWIPT was first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and typical discrete channels. Two co-localized information and power receivers were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between Energy Harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. Dedicated information and energy beamforming were then investigated in \cite{Zhang2013,Park2014} to characterize the R-E region for multi-antenna broadcast and interference channels. On the other hand, \cite{Trotter2009} pointed out that the RF-to-Direct Current (DC) conversion efficiency depends on the rectifier input power level and input waveform shape. It implies that the modeling of the energy harvester, in particular its nonlinearity, has a crucial and significant impact on the waveform preference, resource allocation and system design of any wireless-powered systems \cite{Trotter2009,Clerckx2018,Clerckx2019}. Motivated by this, \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics, then designed joint waveform and beamforming design for WPT. Simulation and experiments demonstrated that ignoring the energy harvester nonlinearity is inaccurate and emphasized the benefit of modeling such nonlinearity in real system design \cite{Kim2019,Kim2020a}. Importantly, the joint waveform and beamforming strategy for WPT was also shown experimentally in \cite{Kim2020} to be a key technique to expand the operation range. Beyond WPT, the work in \cite{Clerckx2016a} was extended to SWIPT in \cite{Clerckx2018b}. Uniquely, it showed that the rectifier nonlinearity leads to radical changes to SWIPT design, namely 1) modulated and unmodulated waveforms are not equally suitable for wireless power delivery, 2) a multi-carrier unmodulated waveform superposed to a multi-carrier modulated waveform is useful to enlarge the R-E region of SWIPT, 3) a combination of PS and TS is in general the best strategy, 4) the optimal input distribution is not the conventional Circularly Symmetric Complex Gaussian (CSCG), 5) the rectifier nonlinearity is beneficial to system performance and is essential to efficient SWIPT design. Those observations, validated experimentally in \cite{Kim2019},  led to the question "what is the optimal input distribution for SWIPT under nonlinearity?". This question was answered in \cite{Varasteh2020} for single-carrier SWIPT, and some attempts were further made in \cite{Varasteh2019d} for multi-carrier SWIPT. The answer sheds new light to fundamental limits of SWIPT and practical signaling (e.g. modulation and waveform) strategies. It is now well understood from \cite{Clerckx2018b,Varasteh2020,Varasteh2019d} that, due to the nonlinearity, a combination of CSCG and On-Off Keying in single-carrier setting and non-zero mean and asymmetric inputs in multi-carrier setting lead to significantly larger R-E region compared to conventional CSCG. Recently, \cite{Varasteh2020a} used machine learning techniques to design SWIPT signaling under nonlinearity to complement the information theoretic results of \cite{Varasteh2020} and new modulation schemes were subsequently designed.
		\end{subsection}

@@

		\begin{subsection}{IRS-Aided SWIPT}
			The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT. It was argued in \cite{Wu2020b} that dedicated energy beam is power-inefficient and may cause interference, thus not required to maximize the Weighted Sum-Power (WSP) for a multiuser IRS-assisted SWIPT system. On the other hand, \cite{Tang2019} suggested that if the interference can be cancelled, multiple energy beams are generally required for the max-min harvested power problem. \cite{Wu2020a} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update transmit precoders and IRS phase shifts while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power because the rank-deficient channels are highly correlated. In such cases, a single energy stream is enough for all energy receivers. However, to the best of the authors' knowledge, all existing IRS-assisted SWIPT papers focus on single-carrier transmission and on an inaccurate and oversimplified linear energy harvester model.

			In this paper, we marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT (accounting for nonlinearity) with the passive beamforming capability of IRS. The contribution of the paper are listed as follows.

			\textit{First}, we introduce a novel IRS-aided SWIPT architecture based on a joint waveform, active and passive beamforming design. This architecture can be seen to IRS-aided SWIPT what \cite{Clerckx2018b} is to SWIPT. Specifically, we consider a multi-carrier IRS-aided downlink MISO SWIPT system where the IRS assists the information and energy transmission of a single user. A multi-carrier unmodulated power waveform (deterministic multisine) is superposed to a multi-carrier modulated information waveform to boost the energy transfer efficiency. The power and information waveforms and active beamforming at the transmitter, the phase shifts at the IRS, and the splitting ratio at the receiver are jointly optimized to maximize the R-E tradeoff while accounting for the rectenna nonlinearity. This is the first paper to propose such a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT. Note that existing IRS-aided SWIPT papers \cite{Wu2020b,Tang2019,Wu2020a,Pan2020} focus on single-carrier transmissions and ignore the rectenna nonlinearity (and therefore assume the oversimplified and inaccurate linear model), which prevents from exploiting the waveform gain in SWIPT system design. On the contrary, this paper focus on multi-carrier IRS-SWIPT and investigates the fundamental impact of harvester nonlinearity on joint waveform, active and passive beamforming design.

			\textit{Second}, we formulate an optimization for this joint waveform, active and passive beamforming design so as to characterize the R-E region achieved by the proposed architecture. The R-E region characterization problem is transformed into multiple energy maximization problems subject to rate constraints. Each achievable R-E pair is obtained through an Alternating Optimization (AO) algorithm that iteratively updates 1) phase shift at the IRS, 2) waveform and active beamforming at the transmitter and power splitting ratio at the receiver, until convergence. On top of the SWIPT optimization based on Geometric Programming (GP) \cite{Clerckx2018b}, our IRS-aided SWIPT optimization employs an low-complexity passive beamforming algorithm based on Successive Convex Approximation (SCA) and Semidefinite Relaxation (SDR), which solves the highly non-convex problem in a efficient and reliable manner. Though no rigorous mathematical proof exists for the convergence of the relaxed IRS phase shift problem, numerical results demonstrated SDR is tight and the proposed algorithm can always find a stationary point for all tested channel realizations under different configurations.

@@

			\textit{Notations:} Scalars are denoted by italic letters, vectors are denoted by bold lower-case letters, and matrices are denoted by bold upper-case letters. $j$ refers to the imaginary unit. $\mathbb{C}^{x \times y}$ denotes the subspace spanned by complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ stand for the real and imaginary part of a complex number or variable, respectively. $(\cdot)^*$, $(\cdot)^T$ and $(\cdot)^H$ represent the conjugate, transpose, and conjugate transpose operators, respectively. $\mathcal{A}\{\cdot\}$ extracts the DC component of a signal, and $\mathcal{E}_X\{\cdot\}$ takes the expectation over the distribution of the random variable $X$ ($X$ may be omitted for simplicity). For a scalar $x$, $\lvert{x}\rvert$ denotes its absolute value. For a vector $\boldsymbol{x}$, $\lVert{\boldsymbol{x}}\rVert$ refers to its Euclidean norm, $\arg(\boldsymbol{x})$ refers to its argument vector, and $\mathrm{diag}(\boldsymbol{x})$ refers to a square diagonal matrix with the elements of $\boldsymbol{x}$ on the main diagonal. For a general matrix $\boldsymbol{M}$, $\mathrm{rank}(\boldsymbol{M})$ denotes it rank. For a square matrix $\boldsymbol{S}$, $\mathrm{Tr}(\boldsymbol{S})$ denotes its trace, and $\boldsymbol{S} \succeq 0$ means that $\boldsymbol{S}$ is positive semi-definite. The distribution of a CSCG random vector with mean vector $\boldsymbol{0}$ and covariance matrix $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$, and $\sim$ stands for "distributed as". We also denote $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ as stationary solution and solution at iteration $i$, respectively.
		\end{subsection}
	\end{section}

@@

		\begin{subsection}{Transmit Signal}
			Denote $\tilde{x}_{I,n}(t)$ as the information symbol transmitted over subband $n$ satisfying $\tilde{x}_{I,n}\sim\mathcal{CN}(0,1)$. The superposed transmit signal on antenna $m$ ($m=1,\dots,M$) at time $t$ is
			\begin{equation}\label{eq:x_m}
				x_m(t)=\Re\left\{\sum_{n=1}^N\left({w_{I,n,m}\tilde{x}_{I,n}(t)}+w_{P,n,m}\right){e^{j2{\pi}{f_n}{t}}}\right\}
			\end{equation}
			where $w_{I/P,n,m}$ denotes the weight of the information and power signal transmitted by antenna $m$ at subband $n$.

			Stacking up the entries on all antennas, we define $\boldsymbol{w}_{I/P,n}=[w_{I/P,n,1},\dots,w_{I/P,n,M}]^T \in \mathbb{C}^{M \times 1}$ and $\boldsymbol{x}(t)=\boldsymbol{x}_{I}(t)+\boldsymbol{x}_{P}(t)$, where
			\begin{align}
				\boldsymbol{x}_{I}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{I,n}\tilde{x}_{I,n}(t){e^{j2{\pi}{f_n}{t}}}\right\}}\,,\label{eq:x_I}\\
				\boldsymbol{x}_{P}(t) &= \Re{\left\{\sum_{n=1}^N\boldsymbol{w}_{P,n}{e^{j2{\pi}{f_n}{t}}}\right\}}\,.\label{eq:x_P}
			\end{align}
		\end{subsection}

		\begin{subsection}{Composite Channel}
			At subband $n$, denote the AP-user direct channel as $\boldsymbol{h}_{D,n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$, and IRS-user reflective channel as $\boldsymbol{h}_{R,n}^H \in \mathbb{C}^{1 \times L}$. At the IRS, element $l$ ($l=1,\dots,L$) redistributes the incoming signal by adjusting the reflection coefficient $\phi_l=\alpha_l e^{j\theta_l}$ with reflection amplitude $\alpha_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$~\footnote{To investigate the performance upper bound of IRS, we suppose the reflection coefficient is maximized $\alpha_l=1\,,\forall l$ while the phase shift is a continuous variable over $[0,2\pi)$.}. Define the IRS matrix as $\boldsymbol{\Theta} = \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ that collects the reflection coefficients onto its main diagonal entries. The extra link introduced by IRS can be modeled as a concatenation of the AP-IRS incident channel, IRS reflection matrix, and IRS-user reflective channel. On top of this, the total composite channel is obtained by superposing the IRS-aided extra channel to the AP-user direct channel as
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{D,n}^H + \boldsymbol{h}_{R,n}^H \boldsymbol{\Theta} \boldsymbol{H}_{I,n} = \boldsymbol{h}_{D,n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where $\boldsymbol{\phi}=[\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{V}_{n}=\mathrm{diag}(\boldsymbol{h}_{R,n}^H)\boldsymbol{H}_{I,n} \in \mathbb{C}^{L \times M}$. Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.
			\begin{remark}
				The IRS reflection coefficients are constant across the frequency, i.e. the IRS is frequency-flat where independent phase shift control over subbands are prohibited due to hardware constraints.
			\end{remark}
		\end{subsection}

@@

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the multisine power waveform creates no interference to the information waveform. Therefore, the achievable rate writes as
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_I,\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{I,n} \rvert^2}{\sigma_n^2}\right)}
			\end{equation}
			where $\rho$ is the power splitting ratio for the energy harvester, $\sigma_n^2$ is the variance of the total noise (at RF-band and during RF-to-baseband conversion) on tone $n$. Rate \eqref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
		\end{subsection}

@@

			To maximize non-concave expression \eqref{eq:z_irs}, we propose a SCA algorithm that approximate the second-order terms by first-order Taylor expansion \cite{Adali2010}. Based on the solution at iteration $i - 1$, the approximations at iteration $i$ are

@@

			which provide lower bounds to the corresponding terms in \eqref{eq:z_irs}. Hence, the objection function is approximated by $\tilde{z}(\boldsymbol{\Phi}^{(i)})$ in \eqref{eq:z_irs_approx}, and problem~\eqref{op:original} is transformed to

@@

			Therefore, problem~\eqref{op:original} is reduced to an amplitude optimization issue

@@

			Since problem~\eqref{op:waveform} involves the production of nonnegative real variables, we introduce auxiliary variables $t',\bar{\rho}$ and transform it into a reversed GP
